Democracy, Public Support, and Measurement Uncertainty

### 2021-06-09 paper/dcpo_demsupport.Rmd
merge conflict avoid

# produced by cls_ajps_apsr_uncertain.R and dcpo_ajps_apsr_uncertain.R
load(here("data", "cls_ajps.rda")) 
load(here("data", "dcpo_ajps.rda")) 
load(here("data", "cls_apsr.rda"))
load(here("data", "dcpo_apsr.rda"))

>>>>

# produced by cls_ajps_apsr_uncertain.R and dcpo_ajps_apsr_uncertain.R
load(here("data", "cls_ajps.rda")) 
load(here("data", "dcpo_ajps.rda")) 
load(here("data", "cls_apsr.rda"))
load(here("data","dcpo_apsr.rda"))
